---
title: "No evidence for familiarity preferences after partial exposure to visual concepts in preschoolers and infants"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{Gal Raz$^1$ (galraz@mit.edu),
    \bf{Anjie Cao$^2$  (anjiecao@stanford.edu)},\\
    \bf{Minh Khong Bui$^3$  (mbui100@csu.fullerton.edu)}, \\
    \bf{Michael C. Frank$^2$ (mcfrank@stanford.edu)},
     and \bf{Rebecca Saxe$^1$ (saxe@mit.edu)} \\
    $^1$Department of Brain and Cognitive Sciences, MIT,
    $^2$Department of Psychology, Stanford University, \\
    $^3$Department of Communicative Sciences and Disorders, California State University, Fullerton \\
    }

abstract: >
  From birth, humans make decisions about what to look at and for how long. A classic framework proposes encoding as a key driver of looking behavior in development - in early stages
  of encoding, infants and young children prefer to engage with
  familiar stimuli, while at
  later stages of encoding they prefer novel
  stimuli. Though this framework is often invoked when interpreting looking time studies, it is rarely validated empirically.
  Here, we test these predictions by explicitly manipulating
  exposure durations within-subjects. While we found
  robust evidence for habituation and novelty preferences, limiting exposure to visual concepts did not result in
  familiarity preferences in any age group. Our findings suggest that
  limited exposure does not generically lead to familiarity preferences, and that interpretations of observed familiarity
  preferences should be made with care. We argue for the development of
  formal frameworks which link the learning problem faced by
  participants to their attentional preferences.
    
keywords: >
    psychology; cognitive development; learning

    
output: 
    cogsci2016::cogsci_paper
    
  
nocite: | 
 

final-submission: \cogscifinalcopy
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```


```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(magrittr)

preschool_d <- read_csv(here("data/preschooler/clean_data.csv"))
preschool_raw_d <- read_csv(here("data/preschooler/merged_data.csv"))

infant_d <- read_csv(here("data/infant/infant_processed_data.csv"))

#Read in cached models 

# preschoolers
preschool_general_mod <- readRDS(here("cached_data/preschooler/preschool_general_mod.Rds"))
fam_mod <- readRDS(here("cached_data/preschooler/fam_mod.Rds"))

# infants
model_1a <- readRDS( here("cached_data/infants/model_1a.rds" ))


model_2a <- readRDS( here("cached_data/infants/model_2a.rds" ))
model_2b <- readRDS( here("cached_data/infants/model_2b.rds" ))
model_2c <- readRDS( here("cached_data/infants/model_2c.rds" ))
model_2d <- readRDS( here("cached_data/infants/model_2d.rds" ))
model_3a <- readRDS( here("cached_data/infants/model_3a.rds" ))
model_3b <- readRDS( here("cached_data/infants/model_3b.rds" ))
model_3c <- readRDS( here("cached_data/infants/model_3c.rds" ))

```



# Introduction 

```{r child = "01_introduction.Rmd"}
```

# Experiment 1 

@hunter1988multifactor posit that younger participants are more likely to
exhibit familiarity preferences after the same amount of exposure to a
stimulus due to their reduced encoding speed. There is some empirical
evidence suggesting that younger infants show familiarity preferences in
tasks in which older infants show novelty preferences [@thiessen2003cues; @cyr2013development]. This age-related change in preferences may explain the lack of familiarity preferences observed in adults [@cao2022habituation; @gustafsson2021visual]. It is possible that adults can process stimuli so fast that even brief exposure is sufficient for completing stimulus encoding. We therefore tested young children in an experimental paradigm that has captured habituation and novelty preferences in adults [Fig. 1: left panel, @cao2022habituation]. 

## Methods

```{r child = "02_experiment1_methods.Rmd"}
```

## Results

```{r child = "03_experiment1_results.Rmd"}
```

# Experiment 2

In the infant paradigm, infants were familiarized to six unique stimuli
for different exposure durations within a single session in a blocked
design (Fig. 1, right panel). We chose this design as a contrast to the standard infant
familiarization/habituation paradigm in which infants are familiarized
to only one stimulus throughout an experiment. In such designs, the effects of exposure duration must be estimated between groups of infants. In contrast, in our design, by presenting individual infants with multiple blocks and varying exposure durations, we
directly measure the effect of prior exposure on looking time, within participants.

To get a dense sample of possible exposure durations, we pre-registered and ran two experiments, sequentially, with two sets of exposure durations. The first experiment showed infants blocks containing 0, 4 or 8 exposure events (Exp A; pre-registered at [this link](https://osf.io/gux4f/?view_only=b4d6d0118dfa41a79fb431d389f4fecc)). The second experiment showed infants blocks containing 1, 3 or 9 exposure events (Exp B; pre-registered at [this link](https://osf.io/w6pgu/?view_only=39ee108159884761a0c5bc68d11918df)).

## Methods

```{r child = "04_experiment2_methods.Rmd"}
```

## Results

```{r child = "05_experiment2_results.Rmd"}

```


# Discussion 

```{r child = "06_general_discussion.Rmd"}
```

# References 

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
