---
title: "No evidence for familiarity preferences after partial exposure to visual concepts in preschoolers and infants"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{Gal Raz$^1$ (galraz@mit.edu),
    \bf{Anjie Cao$^2$  (anjiecao@stanford.edu)},\\
    \bf{Ming Khong Bui$^3$  (mbui100@csu.fullerton.edu)},
    \bf{Michael C. Frank$^2$ (mcfrank@stanford.edu)},
     and \bf{Rebecca Saxe$^1$ (saxe@mit.edu)} \\
    $^1$Department of Brain and Cognitive Sciences, MIT,
    $^2$Department of Psychology, Stanford University, \\
    $^3$Department of Communicative Sciences and Disorders, California State University \\

    }

abstract: >
  
    
keywords: >
    developmental psychology; familiarity prefernces; habituation; learning; attention; cognitive development 

    
output: 
    cogsci2016::cogsci_paper
    
  
nocite: | 
 

final-submission: \cogscifinalcopy
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```


```{r}
library(tidyverse)
library(here)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(magrittr)

preschool_d <- read_csv(here("data/preschooler/clean_data.csv"))
preschool_raw_d <- read_csv(here("data/preschooler/merged_data.csv"))

infant_d <- read_csv(here("data/infant/infant_processed_data.csv"))
# exclude invalid trials
infant_d %<>% filter(!exclude)

#Read in cached models 

# preschoolers
preschool_general_mod <- readRDS(here("cached_data/preschooler/preschool_general_mod.Rds"))
fam_mod <- readRDS(here("cached_data/preschooler/fam_mod.Rds"))

# infants
model_1a <- readRDS( here("cached_data/infants/model_1a.rds" ))


model_2a <- readRDS( here("cached_data/infants/model_2a.rds" ))
model_2b <- readRDS( here("cached_data/infants/model_2b.rds" ))
model_2c <- readRDS( here("cached_data/infants/model_2c.rds" ))
model_2d <- readRDS( here("cached_data/infants/model_2d.rds" ))
model_3a <- readRDS( here("cached_data/infants/model_3a.rds" ))
model_3b <- readRDS( here("cached_data/infants/model_3b.rds" ))
model_3c <- readRDS( here("cached_data/infants/model_3c.rds" ))

```



# Introduction 


```{r child = "01_introduction.Rmd"}
```


# Experiment 1 

@hunter1988multifactor posit that younger participants are more likely to exhibit familiarity preferences for a given stimulus due to their reduced encoding speed. There was empirical evidence showing that younger infants would show familiarity preferences in tasks in which older infants show novelty preferences (Cyr grammar study). This age-related change in preference may explain the lack of familiarity preference observed in adults [@cao2022habituation; Gustafson]. It is possible that adults can process so fast that even brief exposure is sufficient for completing the stimuli encoding. 

To test this age hypothesis, we decided to test young children on an experimental paradigm that has captured habituation and novelty preference in adults [@cao2022habituation]. According to Hunter and Ames (1988), young children should be slower in processing information, making them more likely to show a familiarity preference. 

## Methods

```{r child = "02_experiment1_methods.Rmd"}
```

## Results and discussion

```{r child = "03_experiment1_results.Rmd"}
```

# Experiment 2

## Methods

```{r child = "04_experiment2_methods.Rmd"}
```

## Results and discussion

```{r child = "05_experiment2_results.Rmd"}

```


# General discussion 

```{r child = "06_general_discussion.Rmd"}
```

# References 

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
