## Participants 

```{r}
n_subject_total <- nrow(preschool_raw_d %>% distinct(subject))
n_subject_included <- nrow(preschool_d %>% filter(participant_type == "kids") %>% distinct(subject))

preschool_subject_df <- preschool_d %>% 
   filter(participant_type == "kids") %>% 
  distinct(child_age_group, subject) %>% 
  group_by(child_age_group) %>% 
  count()
```


```{r}
summary_lt_d <- preschool_raw_d %>% 
  filter(trial_type == "stimuli-presentation" & block_background != "null") %>% 
  summarise(
     median = median(log(trial_looking_time)),
    mad = mad(log(trial_looking_time)), 
    upper = median + 3 * mad, 
    lower = median - 3 * mad) 


lower <- preschool_raw_d %>% 
  filter(subject %in% unique(preschool_d$subject)) %>% 
  filter(log(trial_looking_time) < summary_lt_d$lower)

higher <- preschool_raw_d %>% 
     filter(subject %in% unique(preschool_d$subject)) %>% 
  filter(log(trial_looking_time) > summary_lt_d$upper)

total_excluded_trial = (nrow(lower) + nrow(higher))
total_trial <- nrow(preschool_raw_d %>% 
  filter(trial_type == "stimuli-presentation" & block_background != "null"))
percent_excluded = round(total_excluded_trial / total_trial, 4) * 100

```


`r n_subject_total` children completed a task modified from the adult self-paced looking time studies reported in @cao2022habituation. Following our pre-registration ([link](https://aspredicted.org/blind.php?x=5WQ_YQH)), `r n_subject_total - n_subject_included` children were excluded from the analysis because their performance in the attention-check task failed to meet the inclusion criteria (answering 4 out of the 8 attention check questions correctly). We also excluded trials with looking time that were three absolute deviations away from the median in the log-transformed space across participants (Total trial *N* = `r total_trial`; Excluded trial *N* = `r total_excluded_trial`, `r percent_excluded`% of the total trials). The final datasets includes `r n_subject_included` children in total (3yr: N = `r filter(preschool_subject_df, child_age_group == 3)$n`; 4yr: N = `r filter(preschool_subject_df, child_age_group == 4)$n`; 5yr: N = `r filter(preschool_subject_df, child_age_group == 5)$n`). All participants were recruited in a university-affiliated research preschool. 

```{r experimental_design, echo = FALSE, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=7, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.cap = "Experimental design of preschooler and infant experiments. There were four main differences: 1) Preschoolers responded with button presses, infants through lookaways, 2) preschoolers saw background trials after deviants, whereas deviants always appeared at the end in the infant experiments, 3) in preschoolers all trials were self-paced, whereas in infants only the last trial was self-paced and 4) preschooler and infant paradigms used different sets of animate stimuli."}
img <- png::readPNG("figs/experimental_design.png")
grid::grid.raster(img)
```

## Stimuli 

We used a subset of stimuli used in a prior adult self-paced looking time study, a set of animated creatures from the computer game Spore (developed by Maxis in 2008). 

## Procedures 

Children were tested individually in a test room by an experimenter. The
experimenter invited the child to "meet some monster friends" and then
familiarized the child with the laptop computer used to present the
experiment. Before the test, each child went through a practice phase
where they practiced pressing the space bar to move on to the next
trial. The child was instructed that they can press the key and move on
to meet more monster friends whenever they want.


On each trial, the child would see an animated creature appear on the
screen. The child could move on to the next trial by pressing the space
bar. Each block consisted of six trials. Usually, the same creature was shown repeatedly (the background stimulus), but each block could
contain either zero or one deviant trial. Deviant trials were trials
that present a different creature from the background stimulus. Deviant
trials appeared on the second, the fourth, or the sixth trial of the
block. Each child saw eight blocks in total.

At the offset of each block, we presented a memory task to ensure
children were appropriately attending to the task, asking them which of
two creatures they had seen before.

